Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
efficient chatbots changed to effective

Several higher education chatbots' evaluation studies have been 
undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
\cite{Smutny2020} examined 47 educational chatbots implemented in
Facebook Messenger with the focus to identify characteristics and
quality metrics such as language, subject matter and platform. 
Whereas the study undertaken by \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
purpose into service-oriented and teaching-oriented. The first category includes those that
provide service support such as the chatbot Ask Holly \cite{meetholly}
and Dina \cite{santoso2018dinus}; both chatbots respond to students'
questions about enrolment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently
asked questions about timetables, grades, tutors and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
breaking the ice between new students by introducing them to each
other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
university students that is able to answer to their frequently asked
questions. 
For some time, the University of Granada had ELVIRA as a
chatbot in its main web page \cite{MOREO20129}. Besides being able to
answer pre-established (frequent) questions, it did so from the website of the
University of Granada using an inset character, voiced by a real
person, who lip-synced the answers. The emphasis in the case of Elvira,
however, was on the authenticity of the synchronization more than in
making the update of questions and answers simpler, or more
interactive, using actual messaging platforms. 
In most cases, using the inset search engine was able to give you more up-to-date and
accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

>>>>

Several higher education chatbots' evaluation studies have been 
undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
\cite{Smutny2020} examined 47 educational chatbots implemented in
Facebook Messenger with the focus to identify characteristics and
quality metrics such as language, subject matter and platform. 
Whereas study \cite{perez2020rediscovering} aimed to categorise educational chatbots according to their
purpose into service-oriented and teaching-oriented. The first category includes those that
provide service support such as the chatbot Ask Holly \cite{meetholly}
and Dina \cite{santoso2018dinus}; both chatbots respond to students'
questions about enrolment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently
asked questions about timetables, grades, tutors and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
breaking the ice between new students by introducing them to each
other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
university students that is able to answer to their frequently asked
questions. 
For some time, the University of Granada had ELVIRA as a
chatbot in its main web page \cite{MOREO20129}. Besides being able to
answer pre-established (frequent) questions, it did so from the website of the
University of Granada using an inset character, voiced by a real
person, who lip-synced the answers. The emphasis in the case of Elvira,
however, was on the authenticity of the synchronization more than in
making the update of questions and answers simpler, or more
interactive, using actual messaging platforms. 
In most cases, using the inset search engine was able to give you more up-to-date and
accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop effective chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.
